---
title: "Homework 1"
author: "Stephen Powers"
date: 2019-09-10
output: github_document
---

# Problem 1

Create a data frame comprised of:

(1) a random sample of size 8 from a standard Normal distribution
(2) a logical vector indicating whether elements of the sample are greater than 0
(3) a character vector of length 8
(4) a factor vector of length 8, with 3 different factor “levels”

```{r Problem_1, include = FALSE}
library(tidyverse)

first_df = tibble(
  vec_rsamp = rnorm(8),
  vec_logical = vec_rsamp > 0,
  vec_char = letters[1:8],
  vec_factor = rep(c("a","b","c"), length = 8)
)

```

## Calculate Means

```{r}
mean(first_df[["vec_rsamp"]])
mean(first_df[["vec_logical"]])
mean(first_df[["vec_char"]])
mean(first_df[["vec_factor"]])
```
We were able to get the means for vec_rsamp and vec_logical because they are numeric. We were unable to get the mean for vec_char and vec_factor because they are not numeric values.  

```{r}
nvec_logical = as.numeric(first_df[["vec_logical"]])
```
Not sure what this does yet. 
```{r}
nvec_char = as.numeric(first_df[["vec_char"]])
```
This introduces NAs in place of characters by coercion.
```{r}
nvec_factor = as.numeric(first_df[["vec_factor"]])
```
This introduces NAs in place of factorial values by coercion.

(1) Convert the logical vector to numeric, and multiply the random sample by the result

```{r}

```

(2) Convert the logical vector to a factor, and multiply the random sample by the result

```{r}

```

(3) Convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result



# Problem 2


```{r Problem 2}
second_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_logical = x + y > 1,
  vec_numeric = as.numeric(vec_logical),
  vec_factor = as.factor(vec_logical),
)

nrow(second_df)
ncol(second_df)
pull(second_df, x)
mean(pull(second_df, x))
median(pull(second_df, x))
sd(pull(second_df, x))
pull(second_df, y)
pull(second_df, vec_numeric)
pull(second_df, vec_factor)

```
Number of rows = 500 
Number of columns = 5
Mean = 0.03911527
Median = 0.03718347
Standard Deviation = 1.043226

```{r scatter_plot}
ggplot(second_df, aes(x = x, y = y, color = vec_logical)) + geom_point()

ggsave("scatter_plotHW1.pdf")
```

```{r scatter_plot2}
ggplot(second_df, aes(x = x, y = y, color = vec_numeric)) + geom_point()
```

```{r scatter_plot3}
ggplot(second_df, aes(x = x, y = y, color = vec_factor)) + geom_point()
```

All three of the scatter plots look very similar. Logical and factor both use "true" or "false", but numeric is 0 or 1.
