---
title: "Homework 1"
author: "Stephen Powers"
date: 2019-09-10
output: github_document
---

## Problem 1

Create a data frame comprised of:

(1) a random sample of size 8 from a standard Normal distribution
(2) a logical vector indicating whether elements of the sample are greater than 0
(3) a character vector of length 8
(4) a factor vector of length 8, with 3 different factor “levels”

```{r Problem_1, include = FALSE}
library(tidyverse)

first_df = tibble(
  vec_rsamp = rnorm(8),
  vec_logical = vec_rsamp > 0,
  vec_char = letters[1:8],
  vec_factor = rep(c("a","b","c"), length = 8)
)

```

### Calculate Means

```{r}
mean(pull(first_df, vec_rsamp))
mean(pull(first_df, vec_logical))
mean(pull(first_df, vec_char))
mean(pull(first_df, vec_factor))
```
We were able to get the means for vec_rsamp and vec_logical because they are numeric. We were unable to get the mean for vec_char and vec_factor because they are not numeric values.  

```{r}
as.numeric(pull(first_df, vec_logical))
```
This code converts FALSE to 0 and True to 1.
```{r}
as.numeric(pull(first_df, vec_char)) 
```
This introduces NAs in place of characters by coercion.
```{r}
as.numeric(pull(first_df, vec_factor))
```
This introduces NAs in place of factorial values by coercion.

(1) Convert the logical vector to numeric, and multiply the random sample by the result

```{r}
as.numeric(pull(first_df, vec_logical)) * pull(first_df,vec_rsamp) 
```

(2) Convert the logical vector to a factor, and multiply the random sample by the result

```{r}
as.factor(pull(first_df, vec_logical)) * pull(first_df,vec_rsamp) 
```

(3) Convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result

```{r}
as.numeric(as.factor(pull(first_df, vec_logical))) * pull(first_df,vec_rsamp) 
```


## Problem 2

Create a data frame comprised of:
(1) x: a random sample of size 500 from a standard Normal distribution
(2) y: a random sample of size 500 from a standard Normal distribution
(3) A logical vector indicating whether x + y > 1
(4) A numeric vector created by coercing the above logical vector
(5) A factor vector created by coercing the above logical vector

```{r Problem 2}
second_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_logical = x + y > 1,
  vec_numeric = as.numeric(vec_logical),
  vec_factor = as.factor(vec_logical),
)
```

### Inline Code
This data frame has 'nrow(second_df)' rows and 'ncol(second_df)' columns.The mean, median, and standard deviation of the 'x' variable is 'mean(pull(second_df, x))', median(pull(second_df, x)), and sd(pull(second_df, x)).

### Scatter Plots

(1) Logical Scatter Plot 

```{r scatter_plot}
ggplot(second_df, aes(x = x, y = y, color = vec_logical)) + geom_point()

ggsave("scatter_plotHW1.pdf")
```

(2) Numeric Scatter Plot 

```{r scatter_plot2}
ggplot(second_df, aes(x = x, y = y, color = vec_numeric)) + geom_point()
```

(3) Factor Scatter Plot 

```{r scatter_plot3}
ggplot(second_df, aes(x = x, y = y, color = vec_factor)) + geom_point()
```

All three of the scatter plots look very similar. Logical and factor both use "true" or "false", but numeric is 0 or 1.
